---
title: "TEST"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

READING IN CITY MORPHOLOGY DATA 

```{r cars}
morpho <-st_read('city_morpho/GR_UNITS_20190122.shp')
head(morpho)
```
There are a lot of columns - we only need a few.  

READING IN POLLUTION DATA 
```{r cars}
read_csv("winterpol1920/airtube-data-BG-201911.csv.gz") -> nov
nov %>% write_csv("airtube-data-BG-201911.csv")

read_csv("winterpol1920/airtube-data-BG-201912.csv.gz") -> dec
dec %>% write_csv("airtube-data-BG-201912.csv")

read_csv("winterpol1920/airtube-data-BG-202001.csv.gz") -> jan
jan %>% write_csv("airtube-data-BG-202001.csv")

read_csv("winterpol1920/airtube-data-BG-202002.csv.gz") -> feb
feb %>% write_csv("airtube-data-BG-202002.csv")

read_csv("winterpol1920/airtube-data-BG-202003.csv.gz") -> mar
mar %>% write_csv("airtube-data-BG-202003.csv")
head(mar)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
